Hypertension and microbiome

### 2019-09-30 articletwo.Rmd
Deseq

```{r deseq2}
pseq.genus.core.deseq <-  prune_taxa(taxa(pseq.genus.core), pseq.genus)

dds.data <- phyloseq_to_deseq2(pseq.genus.core.deseq,
                               as.formula(sprintf("~ %s + %s", "HT", paste0(var.CL, collapse = "+"))))

ds2 <- estimateSizeFactors(dds.data, type="poscounts")

dds <- DESeq(ds2, fitType='mean', parallel = TRUE, BPPARAM=MulticoreParam(16))

saveRDS(dds, file = "rds/dds.rds")
#dds <- readRDS(file = "rds/dds.rds")

results(dds) %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    dplyr::filter(qval < 0.05) %>%
    kable
```

>>>>

```{r deseq2}
if (!file.exists("rds/dds.rds")) {
    pseq.genus.core.deseq <-  prune_taxa(taxa(pseq.genus.core), pseq.genus)
    dds.data <- phyloseq_to_deseq2(pseq.genus.core.deseq,
                                   as.formula(sprintf("~ %s + %s",
                                                      paste0(var.CL, collapse = "+"),
                                                      "HYPERTENSION")))

    dds.data <- phyloseq_to_deseq2(pseq.genus.core.deseq, ~HYPERTENSION)

    dds <- DESeq(dds.data, test="Wald", fitType="parametric", parallel = TRUE, BPPARAM=MulticoreParam(16))
    saveRDS(dds, file = "rds/dds.rds")
} else {
    dds <- readRDS(file = "rds/dds.rds")
}
```

## DeSeq

```{r deseq results table}
results(dds, contrast = c("HYPERTENSION", 0, 1)) %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    dplyr::filter(qval < 0.05) %>%
    kable
```

```{r deseq plot}
g.deseq <- results(dds, contrast = c("HYPERTENSION", 0, 1)) %>%
    as.data.frame %>%
    tibble::rownames_to_column("Feature") %>%
    dplyr::mutate(qval = p.adjust(pvalue, method="BH")) %>%
    dplyr::filter(qval < 0.05) %>%
    ggplot(aes(x=Feature, y=log2FoldChange, color=qval)) +
    geom_point(size=1) +
    geom_hline(yintercept = 0, color = "gray") +
    theme(axis.text.x = element_text(angle = -90, hjust = 0, vjust=0.5)) +
    coord_flip() +
    theme_classic()

ggsave(file = "cache/deseq.png", plot=g.deseq, height=10, width=5)
```

<img src = "cache/deseq.png" />
